\section{Objective and Significance}

The traditional memory technologies, e.g. SRAM, DRAM, and Flash memory, played a very important role in the modern computing system and portable multimedia device industries. However, the scaling of the traditional memories is facing significant challenges from process variations and device reliability at 22nm technology and below~\cite{ITRS07,Kinam07}.
In recent years, significant efforts and resources have been put on the researches and developments of \textbf{emerging non-volatile memory (NVM) technologies} that combine attractive features such as scalability, fast read/write, negligible leakage, and non-volatility. Multiple promising candidates, such as \emph{Phase-Change RAM (PCRAM)}, \emph{Magnetic RAM (MRAM)}, \emph{Resistive RAM (RRAM)} and \emph{Memristor}, have gained substantial attentions and are being actively pursued by industry~\cite{ITRS07,burr:scm08}.

The main objective of this 3-year project is to investigate design methodologies and circuit techniques for emerging NVMs in order to enable the massive production and to accelerate the commercialization of these emerging memory technologies. The proposed program makes the following major contributions.

\vspace{5pt}
\squishlist
\item {\textbf{Design methodologies for emerging NVMs:} The device models for emerging NVMs will be built to fill the gap between process development and circuit design. Memory design flow and optimization methodologies will be developed to facilitate the design space explorations.}
\item {\textbf{Circuit techniques for emerging NVM technologies:} Various circuit techniques will be proposed to improve the reliability (including lifetime improvement and variation mitigation), yield, and density.}
\item {\textbf{Integrated educational plan:} The educational plan will enhance the existing standard curricula by integrating new course modules on emerging NVMs to complement and upgrade the core device and circuit design courses, and bring the awareness of emerging memory technologies into the circuit design and computer architecture community through tutorials and workshops.}
\squishend
\vspace{5pt}

The proposed work will initiate a novel research direction in memory design by developing NVM device models and design methodologis, inventing novel memory structures and circuit techniques, and study the design implications on future computing systems. The work will support the deployment of modern microprocessor and embedded system designs that utilize emerging NVM technologies. The proposed research will provide a complementary perspective to the existing computing system researches.

