\section{Objective and Significance}

The traditional memory technologies, e.g. SRAM, DRAM, and Flash memory, played a very important role in the development of modern computing system and portable multimedia device industries. However, the further scaling at 32nm technology node and below is facing significant technical difficulties, such as large process variations, high leakage power consumption, increased capacitive coupling between adjacent cells, and the device endurance and retention issues~\cite{ITRS07,Kinam07}.

In recent years, significant efforts and resources have been put on the researches and developments of \textbf{emerging non-volatile memory (NVM) technologies} that combine attractive features such as scalability, fast read/write, negligible leakage, and non-volatility. Multiple promising candidates, such as Phase-Change RAM (PCRAM), Magnetic RAM (MRAM), Resistive RAM (RRAM), and Memristor, have gained substantial attentions and are being actively pursued by industry~\cite{ITRS07,burr:scm08}.

 The main objective of this 3-year project is to investigate modeling and design techniques for emerging NVMs in order to enable the massive production and to accelerate the commercialization of these emerging memory technologies. The proposed program makes the following major contributions.

\vspace{5pt}
\squishlist
\item {\textbf{Developing device models:} The device models for emerging non-volatile memories (NVMs) will be developed to fill the gap between process development and circuit design society.}
\item {\textbf{Proposing novel circuits solutions:} Based on the unique device characteristics of NVMs, the proposed circuit schemes could benefit from the advantages and make up the shortfalls of NVMs.}
\item {\textbf{Integrated educational plan:} The educational plan will enhance the existing standard curricula by integrating new course modules on emerging NVMs to complement and upgrade the core device and circuit design courses, and bring the awareness of emerging memory technologies into the circuit design and computer architecture community through tutorials and workshops.}
\squishend
\vspace{5pt}

The proposed work will initiate a novel research direction in memory design by integrating NVM devices into the standard memory design flow, inventing novel array structure and circuit techniques, and investigating the impact to future computing system. The work will support the deployment of modern microprocessor and embedded system design that use emerging NVM technologies. The proposed research will provide a complementary perspective to the existing computing system research.

